---
title: "A UN Report on the Relationship between GDP and Life Expectancy"
author: "Grace Kenney"
date: "19 Oct. 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

* Table of Contents
  + Introduction
  + Plots
  + Tables
  + Subsetting Data for Tables
  
**Table of Contents:**

  1. [Introduction](#introduction)
  2. Plots
  3. Tables
  4. Subsetting Data for Tables

## R Markdown

```{r packages, include=FALSE}
library(tidyverse)
```

# Introduction

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r data}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
head(gapminder_1997)
```

```{r gdp_lifeexp_1997, echo=FALSE}
ggplot(data = gapminder_1997) + 

  aes(x = gdpPercap, y = lifeExp, color=continent, size=pop/1000000) + 

  geom_point() +

  labs(x = "GDP Per Capita", y = "Life Expectancy",

       title= "Do people in wealthy countries live longer?", size="Population (in millions)")
```

```{r}
n_countries <- length(unique(gapminder_1997$country))
gdp_min <- min(gapminder_1997$gdpPercap)
gdp_max <- max(gapminder_1997$gdpPercap)
```


|Summary of Data|
|------|------|
|Number of Countries|142|
|Minimum GDP per capita|312|
|Maximum GDP per capita|4.1283 &times; 10<sup>4</sup>|


|Summary of Data|
|------|------|
|Number of Countries|`r n_countries`|
|Minimum GDP per capita|`r gdp_min`|
|Maximum GDP per capita|`r gdp_max`|


```{r}
# use piping to get Oceania countries

oceania <- gapminder_1997 %>%
  filter(continent == "Oceania")

oceania2 <- gapminder_1997[ gapminder_1997$continent=="Oceania", ]

knitr::kable(oceania2)

```




```{r}

# Create table of the countries in the data set forom Oceania
knitr::kable(oceania)

```

```{r}
pop_gt_3M <- gapminder_1997 %>%
  filter(pop > "30000000")

knitr::kable(pop_gt_3M, caption="caption", label="label")
```


Heading? Subheading? Subsubheading?
# Heading
## Sub heading
### Sub sub heading

* Bullet
* list

1. numbered
2. list


$$ GDP = \beta_0 + \beta_1 (LE) + e $$

## Inserting figures

!Caption for awesome plot(figures/awesome_plot.jpg)

